\documentclass[11pt, onecolumn]{article}
\newcommand{\myreferences}{C:/workspace/github/bibliography-jgr/bibliojgr}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{fancyhdr}
\pagestyle{myheadings}
\usepackage{float}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{textcomp}  %for degree symbol
\usepackage{natbib}
\usepackage{breakcites}
\usepackage{amsmath,amssymb}
%\usepackage{apacite}
\usepackage[table]{xcolor}
\definecolor{lightgray}{gray}{0.9}
\usepackage{multirow} 
\usepackage[affil-it]{authblk}  %package for multiple authors
%\graphicspath{{C:/workspace/figures/}}
\graphicspath{{C:/workspace/figures/}}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern} % load a font with all the characters
\newcommand*{\addheight}[2][.5ex]{%
\raisebox{0pt}[\dimexpr\height+(#1)\relax]{#2}%
}
\begin{document}
\def\mean#1{\left< #1 \right>}
\title{Power based analysis in the hypnotic condition versus resting state eyes closed}
%Boredom begets creativity or why predictive coding is not enough to explain intelligent behavior
%An overarching principle of intelligent behavior}

\author[1]{Jaime Gomez-Ramirez\thanks{Corresponding author \hspace{0.6cm} jaime.gomez-ramirez@sickkids.ca}}
\author[2]{}%\thanks{\hspace{0.6cm} tommaso.costa@unito.it}
\affil[1]{The Hospital for Sick Children, Department of Neuroscience and Mental Health, University of Toronto, Bay St. 686, Toronto, (Canada)}
\affil[2]{}

%\twocolumn[
%\begin{@twocolumnfalse}
\date{}
\maketitle

\begin{abstract}

\end{abstract}
%\end{@twocolumnfalse}
%]
\section{Introduction}
\label{se:intro}

\section{Methods}
\label{se:methods}
% show diff btw h and l
% build variance covariance matrix and distance matrix, one for each band
% are they statistically different groups- Multivariate analysis
% meand differences,variability , pca and multidimensionality analysis. clustering?
%connectivity, graph theory?
% spectral analysis?

\subsection{Tests of significance}
For a set of p variables $\{X_1 ... X_p\}$ obtained by measurements over a set of n individuals, if the individuals (patients) belong to two different groups, in our case, high and low hypnotizability, a question of interest is whether the mean of some  variable is the same for either of the two groups. Thus, we have now two samples, $n_1$ and $n_2$ for the high and low hyponotizability patients respectively, the question is whether the two samples are significantly different in the sense that the observed mean difference is so large that is unlikely that to have occurred if the population means are equal (t-test). 
A test to detect the to sample means (for groups H and L) involves calculating the t-statistic.This test is very robust if the variable is normally distributed and for sample sizes sufficiently big (e.g. 20) (note that the test is particularly robust if the samples have equal or very similar size \citep{carter_effect_1979s},\citep{coombs_univariate_1996} , this is not our case, so caveat t-test). The t-test can be done for each of the p variables  $\{X_1 ... X_n\}$ or measurements and decide which of these variables have different mean values for the 2 groups (samples).

\subsubsection{Tests of significance}
Here we address the question of whether there is any difference
between the H and the L hypnotizability patients with respect to the mean values of variables (power correlation of each electrode with the other electrodes). Since the patients (samples) have a different number of variables or measurements (electrodes) we need to take a subset of samples that share those measurements. (bi temporal, monto temporal or hippocampal).
Let us assume that patients 1 and 2 are H and patients 3 to 10 are L. The variables are 
$\{X_1 ... X_p\}$ which are the electrodes that the 10 patients have in common.
For each variable x (e.g. LHD1)
, we calculate the mean for each group $\mean{x_H}$ and $\mean{x_L}$ and the sample variances $s^2_H$ and $s^2_L$. The pool variance is $s^2= (n_H-1)s^2_H + (n_L-1)s^2_L)/(n_H+n_L -1)$ and the t-statistic is $t= (\mean{x_H} - \mean{x_L})/\sqrt(s^2(n_H^{-1} + n_L^{-1}))$, if the t statistics is not significantly different from 0 there is no justification to separate the population in those two groups for that variable. Below we show the results for the tasks taken individually for each variable.
%for which elctrode if any there is evidence of a population mean difference
%between survivors and nonsurvivors
%Table 1 

If we take all the variable taken together 
%Table 2 





More interesting is to study whether all the variables taken together justify splitting the population (the n patients) in two sample groups (high and low). To that end we needa multivariate test, e.g. Hotelling's $T^2$-test which is  the square of the t-test.
In general there will be p variables $\{X_1 ... X_n\}$ two samples of $n_1$ and $n_2$ elements with two sample mean vectors $\mean(x) = \mean(x_1) ...\mean(x_p)$ and two sampe covariance matrixes $C_1$ and $C_2$.   A large Hotelling's $T^2$-test means that the two population mean vectors are different. 
%pg 38Bryan Manly for the frmula of this statistic
%note that The two samples being compared using the t^2 are assumed to
%come from multivariate normal distributions with equal covariance matrices
%If the two population covariance matrices are very different, and
%if sample sizes are very different as well, then a modified test can be used
%(Yao, 1965), but this still relies on the assumption of multivariate normality

\subsection*{Multidimensional scaling}
Multidimensional scaling (MDS) represents proximity data (measures of similarity, e.g. physical closeness, correlation,relatedness etc. ) as distances in a multidimensional space. The MDS algorithm moves the points iteratively so that the fit between distances and data is improved until no further improvement seems possible \citep{borg_modern_2005}.


pg 166 "If road distances were proportional to geographic distances, it would be possible to recover the true map exactly by using a two-dimensional analysis". We take on this idea to study whether we can reconstruct the physical connection of electrodes (the actual implant) from the functional connectivity (per frequency band, power based or phase based). The fc = pc + delta (the functional connectivit is at least the physical connectivity, delta >0 when thee isnot a direct functional link between two electrodes).Therefore, "
all that can be hoped for is a rather approximate recovery of the
physical implant (by only knowing the functional one)" \citep{manly_multivariate_2004}

%For monotonic regression http://www.mathworks.com/matlabcentral/fileexchange/47196-graph-based-clustering-and-data-visualization-algorithms/content/improve_JP/toolbox_imp_JP/lsqisotonic.m
%For euclidean distance between matrices:  http://www.mathworks.com/matlabcentral/fileexchange/47196-graph-based-clustering-and-data-visualization-algorithms/content/improve_JP/toolbox_imp_JP/L2_distance.m

Here we start from the physical distance matrix M, defined as the euclidean distance between any two intracraneal electrodes. Thus $M_{ij}(P) = \sqrt{(x_i - x_j)^2 + (y_i - y_j)^2 + (z_i - z_j)^2}$, where P denotes the physical configuration of n electrodes in a 3 dimensional space, i and j any two electrodes and $x_i,y_i,z_i$ is the
value of electrode point i on the coordinate axis x, y and z respectively. (The previous formula can be generalized with the Minkowski distance equation).
Now the same set of objects can defined a different relationship other than the physical euclidean distance, for example the power-based connectivity correlation, the phase based connectivity correlation etc. We then define $M_{ij}(F)$  where F denotes the functional correlation of the same n electrodes in a 1 dimensional space.
We calculate the monotonic regression of $M_{ij}(F)$ in $M_{ij}(P)$. The best estimated  estimated matrix $\hat{M_{ij}}(F)$ is the one the distance to $M_{ij}(P)$
%, note that $M_{ij}(P)$ is a fixed and uniqueonce the metric space is defined, and $M_{ij}(F)$ consists

First, we calculate $M_{ij}(P)$, we use the euclidean distance, note that there is only one physical configuration matrix for each patient.

Second for each patient, condition and frequency band we calculate $M_{ij}(F)$ whcih defines the functional connectivity matrix according to some correlation criterion, for example power correlation, phase lag index etc.

Third, we calculate the monotonic regression of  $M_{ij}(F)$ to fit $M_{ij}(P)$ to obtain $\hat{M_{ij}}(F)$. Finally we calculate the distance between $M_{ij}(P)$ and $\hat{M_{ij}}(F)$, we do this for each correlation criterion, frequency band, condition and patient in order to asses which functional configuration is closer to the metric (Euclidean) space defined by the intra craneal implant $M_{ij}(P)$.




\section{Results}
\label{se:results}



\bibliographystyle{apalike}
%\bibliographystyle{apacite}
\bibliography{C:/workspace/github/bibliography-jgr/bibliojgr}

\end{document}


\newpage
\section*{Supporting Information}
\label{se:suppinf}

\subsection*{S1 Appendix}
